\begin{rSection}{Presentations}

% Presentations
\begin{pubSubsectionNum}{}
  \item Agency for Defense Development (ADD), Jan., 2022.

  \item Samsung Advanced Institute of Technology, Dec., 2021.

  \item The School of Civil, Architectural Engineering, and Landscape Architecture
Sungkyunkwan University (SKKU), Nov., 2021.

  \item Hanwha Defense, Nov., 2021.

  \koronly{\item 삼성미래기술연구회, Oct., 2021.}

  \koronly{\item Keynote speech, 한국로봇학회, May., 2021.}

  \item KAUST Research Conference on Robotics and Autonomy, Mar., 2021.

  \koronly{\item Keynote speech, 대한기계학회, Dec., 2020.}

  \item Keynote speech, Workshop on Emerging Learning and Algorithmic Methods for Data Association in Robotics, ICRA, Paris, May, 2020.

  \item KAIST School of Computing Colloquium, Apr., 2020.

  \koronly{\item 인공지능 워크샵, 충남대학교, Jan., 2020.}

  \item \ac{ACFR}, Sydney, Austrailia, Nov., 2019.

  \item Keynote speech, AutoNUE Workshop \ac{ICCV}, Seoul, Korea,  Nov., 2019.

  \item Keynote speech, \ac{ICCAS}, Jeju, Korea, Oct., 2019.

  \item Mechanical Engineering, \ac{KAIST}, Daejeon, Korea, Oct., 2019.

  \item Keynote speech, A Robotic State of Mind Workshop, Holomatic, Wuhan, China, Jun., 2019.

  \item KAIST--NAVER Clova AI Workshop, \ac{KAIST}, Daejeon, Korea, Jun., 2019.

  \item Keynote speech, Workshop on Underwater Robotics Perception, ICRA, Montreal, Canada, May, 2019

  \item AI+X Forum, School of Computing, \ac{KAIST}, Daejeon, Korea, May., 2019.

  \item SW Contents Research Laboratory, \ac{ETRI}, Daejeon, Korea, May., 2019.

  \item Mechanical Engineering, \ac{SNU}, Seoul, Korea, May., 2019.

  \item Czech technical university in Prague, Prague, Czech Republic, Apr., 2019.

  \item Department of Naval Architecture \& Ocean Engineering, \ac{PNU}, Busan, Korea, Feb., 2019.

  \koronly{\item Edu4.0 적용사례소개, KAIST 신임교원워크샵, KAIST, Nov., 2018}

  \koronly{\item Keynote speech 국제 필드로봇 포럼, 한국로봇산업진흥원, Nov., 2018}

  \koronly{\item 기조강연, 추계학술대회 한국수중수상로봇기술연구회, Nov., 2018}

  \koronly{\item 카이스트 대학 진로탐색캠프 특강, 과학영재교육연구원, Oct., 2018}

  \item Keynote speech, IEEE International Conference on Ubiquitous Robots, Honolulu, USA, Jun., 2018.

  \item Women in Science and Engineering Session, ICROS Spring Conference, \acf{ICROS}, May., 2017.

  \item Civil and Environmental Engineering, \ac{HKUST}, Hong Kong, Jan., 2017.

  \item Invited talk, Korea Intellectual Property Office, Daejeon, Aug., 2016.

  \item Hyundai Engineering \& Construction, Jul., 2016.

  \item \ac{KICT}, Seoul, Mar., 2016.

  \item Autonomous Systems Lab, ETH Zurich, Feb., 2016.

  \item Keynote speech, ICROS-KROS Joint Spring Conference, \ac{ICROS}, Daejeon, May., 2015.

  \item Daegu-Gyeongbuk Research Center, \ac{ETRI}, Daegu, Korea, Feb., 2015.
  \item Mechanical Engineering, \ac{PNU}, Busan, Korea, Oct., 2014.
  \item Digital Media Engineering, Busan University of Foreign Studies, Busan, Korea, Oct., 2014.
  \item Civil and Environmental Engineering, \ac{KAIST}, Daejeon, Korea, Apr., 2014.
  \item \ac{KRISO}, Daejeon, Korea, Nov., 2013.
  \item Mechanical Engineering and Aerospace Engineering, \ac{SNU}, Seoul, Korea, Sep., 2012.
  \item Samsung Heavy Industries Research Institute, Daejeon, Korea, Sep., 2012.
  \item Mechanical Engineering / Ocean and Resource Engineering, University of Hawaii, Honolulu, HI, USA, Sep., 2012.
  \item Ocean Systems Engineering, \ac{KAIST}, Daejeon, Korea, Nov., 2010.
\end{pubSubsectionNum}

\end{rSection}
